---
title: "Coding1_team_assignment"
author: "Adam Kovacs"
date: "11/2/2021"
output: 
  html_document:
    df_print: paged
  pdf_document:
    extra_dependencies: float
---


```{r setup, include=FALSE}
#import packages
library(tidyverse)
library(modelsummary)
library(kableExtra)

# import data
df_orig <- read_csv( 'https://raw.githubusercontent.com/kovaad/ECBS-5208-Coding-1-Business-Analytics/master/data/DA1_data_Paris_HW1.csv' )

View(df_orig)


```

## Introduction

This is a report on the price collection project of the Paris team for the Data Analysis 1 course in the MS in Business Analytics programme of the Central European University. 

HERE COMES THE MOTIVATION WHY THIS IS A MEANINGFUL PROJECT AND WHAT IS THE MAIN GOAL!

To see the raw data collected: <https://raw.githubusercontent.com/kovaad/ECBS-5208-Coding-1-Business-Analytics/master/data/DA1_data_Paris_HW1.csv>.

## Data

HERE COMES A DETAILLED EXPLANATION ABOUT WHERE THE DATA COMES FROM AND IF IT IS REPRESENTATIVE OR NOT.


```{r, echo=FALSE}
P95 <- function(x){quantile(x,0.95,na.rm=T)}
P05 <- function(x){quantile(x,0.05,na.rm=T)}
datasummary( (`Coke` = Price_cola ) + (`Sport bar` = Price_sport )  ~
             Mean + Median + SD + Min + Max + P05 + P95 , 
             data = df_orig,
             title = 'Descriptive statistics of prices',
             notes = 'Data is available from: https://github.com/kovaad/ECBS-5208-Coding-1-Business-Analytics/blob/master/data/DA1_data_Paris_HW1.csv' ) %>% 
  kableExtra::kable_styling(latex_options = "hold_position")
```

DESCRIPTION OF THE SUMMARY STATS: WHAT CAN WE LEARN FROM THEM?

As the focus is the price of coke and price of sport bar, the Figures below shows the histogram for this variable.

```{r, echo = FALSE, warning=FALSE, fig.width=4, fig.height = 3, fig.align="center" }

ggplot( data = df_orig ) +
  geom_histogram( aes( x = Price_cola ) , fill = 'navyblue'  , bins = 10 ) +
  labs(x = "Price of cola",
       y = "Relative Frequency" )# +
  #xlim(-4,4) +
 #theme_bw()

```

DESCRIPTION OF THE FIGURE. WHAT DOES IT TELS US?

Explain why we have chosen such graph and bandwidth/number of bin

## Conclusion

Write 1-2 sentence, what we can learn from this exercise.
